Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)

### 2014-02-24 paper.tex
Further emphasised the hypothetical nature, even changing the title.

\title{Designing a Search Application for the British Broadcasting Corporation (BBC) Using UML}
\author{Ross Fenning\inst{1}
  \and Huseyin Dogan\inst{2}
  \and Keith Phalp\inst{2}}
\institute{BBC, UK \email{Ross.Fenning@bbc.co.uk}
  \and Bournemouth University, UK \email{\{hdogan,kphalp\}@bournemouth.ac.uk}}

@@

Whilst the BBC website currently has a
functional search feature already, this paper assumes building a new search application
from the ground up so as to give full freedom to apply the analysis and design
techniques therein. In practice, there are engineering challenges involved
in maintaining and building on top of existing systems. Such challenges
are out of scope for this paper.

>>>>

\title{Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)}
\author{Ross Fenning\inst{1}
  \and Huseyin Dogan\inst{2}
  \and Keith Phalp\inst{2}}
\institute{BBC, UK \email{Ross.Fenning@bbc.co.uk}
  \and Bournemouth University, UK \email{\{hdogan,kphalp\}@bournemouth.ac.uk}}

@@

Whilst the BBC website currently has a
functional search feature already, this paper assumes building a new search application
from the ground up so as to give full freedom to apply the analysis and design
techniques therein. In practice, there are engineering challenges involved
in maintaining and building on top of existing systems. Such challenges
and details of the existing infrastructure are out of scope for this paper.
